Generate Random Forest Models

### 2023-12-31 scripts/generate_RF_models.Rmd
all models take

```{r read in response}
p <- '../data/raw/occurrence/combined_records'
p2f <- file.path(p, list.files(p, pattern = '.shp$'))
train_dat <- lapply(p2f, sf::st_read, quiet = TRUE)
train_dat <- bind_rows(train_dat) %>% 
  st_transform(crs(layers))

@@

>>>>

```{r read in response data and model}
p <- '../data/raw/occurrence/combined_records'
p2f <- file.path(p, list.files(p, pattern = '.shp$'))
train_dat <- lapply(p2f, sf::st_read, quiet = TRUE)
train_dat <- bind_rows(train_dat) %>% 
  st_transform(crs(layers))

@@

```{r summarize results from RF models}

psum <- '../results/summary'
f <- file.path(psum, list.files(psum))

summary <- lapply(f, read.csv)
names(summary) <- gsub('.csv', '',  basename(f))
summary <- data.table::rbindlist(summary, idcol = 'species')

filter(summary, Metric == 'Balanced Accuracy') %>% 
  ggplot(aes(x = Value)) + 
  geom_histogram() +
  geom_density()

filter(summary, Metric == 'Sensitivity') %>% 
  ggplot(aes(x = Value)) + 
  geom_histogram()
```
